Draft

### 2020-07-21 Draft.Rmd
fixed formattable table for descriptive analysis problem

```{r}
sum <- data.frame(Stock="S&P500",Min=-0.1276522,Median=0.0006105,Mean=0.0002453,Max=0.1095720,Skewness= -0.3807978,Kurtosis=13.5123,JB.Test=27772,LB.Test=60.627)
formattable(sum)
```

@@

```{r}
sum <- data.frame(Series="Log(VIX)",Min = 2.213, Median = 2.916, Max = 4.415,Skewness= vixsk,Kurtosis=vixkt,JB.Test=415.06,LB.Test=11744)
formattable(sum)
```

>>>>

```{r}
sum <- data.frame(Stock="S&P500",Min=-0.1276522,Median=0.0006105,Mean=0.0002453,Max=0.1095720,Skewness= -0.3807978,Kurtosis=13.5123,JB.Test=27772,LB.Test=60.627)
sum %>% 
  kable("latex",booktabs = T) %>% kable_styling("bordered")
```

@@

```{r}
sum <- data.frame(Series="Log(VIX)",Min = 2.213, Median = 2.916, Max = 4.415,Skewness= vixsk,Kurtosis=vixkt,JB.Test=415.06,LB.Test=11744)
sum %>% 
  kable("latex",booktabs = T) %>% kable_styling("bordered")
```
